Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2011-12-20 extended_catalog/paper/extended_catalog.tex
neew draft v7
better description of diffuse sysetmatics

It is not expected that this diffuse model is superior to the standard
LAT model obtained through an all-sky fit.  However, adding degrees of
freedom to the background model can remove likely spurious sources that
correlate with features in the Galactic diffuse emission.  Therefore,
this tests systematics that may be due to imperfect modeling of the
diffuse emission in the region. Nevertheless, 
this alternative approach to modeling the diffuse emission
does not test all systematics related to the diffuse emission model.
In particular, because the alternative approach uses the same underlying gas
maps it is unable to be used to assess systematics due to mischaracterization of local
diffuse structure due to lack of resolution of the underlying maps.

>>>>

It is not expected that this diffuse model is superior to the standard
LAT model obtained through an all-sky fit.  However, adding degrees of
freedom to the background model can remove likely spurious sources that
correlate with features in the Galactic diffuse emission.  Therefore,
this tests systematics that may be due to imperfect modeling of the
diffuse emission in the region. 
Nevertheless, this alternative approach to modeling the diffuse emission
does not test all systematics related to the diffuse emission model. In
particular, because the alternative approach uses the same underlying gas
maps, it is unable to be used to assess systematics due to insufficient
resolution of the underlying maps. Structure in the diffuse emission that
is not correlated with these maps will also not be assessed by this test.
